---
title: "Analysis of Transmission Types to Fuel Efficiency"
author: "Qingcheng"
date: "Wensday, August 27, 2014"
output:
  html_document:
    keep_md: yes
geometry: margin=0.50in
fontsize: 11pt
---


## Executive Summary
Fuel consumption always to be one of major considerations when purchasing a new vehicle. In this report, we will exploring the [Motor Trend Car Road Tests][1] datasets in R to analyze the influence of some factors to fuel efficiency, especially the influence of transmission types(automatic vs manual) on miles per gallon(MPG).


## Model Selection

First, we load the data from R package dataset, and convert variables transmission types(am) and number of cylinders(cyl) to factors. Then give T test of mpg for two transmission types.

```{r}
data(mtcars)
mtcars$cyl <- factor(mtcars$cyl)
mtcars$am <- factor(mtcars$am, levels=c(0,1), labels=c('auto', 'manual'))
t.test(mtcars$mpg[mtcars$am=='auto'],mtcars$mpg[mtcars$am=='manual'])
```

Then we know that MGP appears to be higher for manual transmission. And p-value less than 0.05.


Then we compare two linear model to see the influence of factors on miles per gallon.

```{r}
model1 <- lm(mpg ~ am, data = mtcars)
model2 <- lm(mpg ~ am + hp + wt, data = mtcars)
summary(model1)$coefficients
summary(model2)$coefficients
```

We can see that for model1, the p-value < 0.001, seems to be exist significant relationship. For model2, we add the `hp` and `wt` to be predictors, the p-value become larger.

From residual QQ plots in figure 2(see Appendix), we can know that the residuals is approximately normally distributed. 

## Appendix 

Figure 1 boxplot of `mpg` respect to `am`.  
```{r}
boxplot(mpg ~ am, data=mtcars, col="green",
        ylab="Miles Per Gallon", main="MPG of 1974 Motor Trend Cars")
```


Figure 2 Residual plots.

```{r}
par(mfrow = c(2, 2))
plot(model2)
```



[1]:http://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html
